Bachelor thesis

### 2020-03-05 experiments.Rmd
Minor additions to code

```{r}
library(mice)
library(mvtnorm)
```

```{r}
#Setting vals for multivariate continous vars
mu = 8
sigma = 2
help(mvtnorm)
```

```{r}
#Generating binary data
n = 1000
binary_categorical_vector = round(runif(n, min = 0, max = 1))
```

>>>>

```{r}
library(mice)
library(mvtnorm)
library(MASS)
```

```{r}
#Setting number of entries
n = 1000
```

```{r}
#Setting vals for multivariate continous vars
mu = replicate(14,0)
tez = matrix(c(1, replicate(10,0)), c(2, replicate(9, 0), 3), nrow=2, ncol=11)
tez
#Variables only correlated with Y
sigmaNoCrossCorr = matrix(c(c(1,  0.4, 0.6, 0.8, 0.1, 0.1, 0.1, 0.2, 0.2, 0.2, 0.4, 0.4, 0.8, 0.8),
          c(0.4, 1, replicate(12, 0)),
          c(0.6, 0,  1, replicate(11,0)),
          c(0.8, 0, 0, 1, replicate(10,0)),
          c(0.1, replicate(3,0), 1, replicate(9,0)),
          c(0.1, replicate(4,0), 1, replicate(8,0)),
          c(0.1, replicate(5,0), 1, replicate(7,0)),
          c(0.2, replicate(6,0), 1, replicate(6,0)),
          c(0.2, replicate(7,0), 1, replicate(5,0)),
          c(0.2, replicate(8,0), 1, replicate(4,0)),
          c(0.4, replicate(9,0), 1, replicate(3,0)),
          c(0.4, replicate(10,0), 1, replicate(2,0)),
          c(0.8, replicate(11,0), 1, 0),
          c(0.8, replicate(12,0), 1)), nrow=14, ncol=14)
sigmaNoCrossCorr

#variables correlated with eachother, still under construction
sigmaCrossCorr = c(c(1,  0.4, 0.6, 0.8, 0.1, 0.1, 0.1, 0.2, 0.2, 0.2, 0.4, 0.4, 0.8, 0.8),
          c(0.4, 1, replicate(12, 0)),
          c(0.6, 0,  1, replicate(11,0)),
          c(0.8, 0, 0, 1, replicate(10,0)),
          c(0.1, replicate(3,0), 1, replicate(9,0)),
          c(0.1, replicate(4,0), 1, replicate(8,0)),
          c(0.1, replicate(5,0), 1, replicate(7,0)),
          c(0.2, replicate(6,0), 1, replicate(6,0)),
          c(0.2, replicate(7,0), 1, replicate(5,0)),
          c(0.2, replicate(8,0), 1, replicate(4,0)),
          c(0.4, replicate(90,0), 1, replicate(3,0)),
          c(0.4, replicate(10,0), 1, replicate(2,0)),
          c(0.8, replicate(11,0), 1, 0),
          c(0.8, replicate(12,0), 1))
mvnData = mvrnorm(n = n, mu, sigmaNoCrossCorr, tol = 1e-14)
```

```{r}
#Generating binary data

binary_categorical_vector = round(runif(n, min = 0, max = 1))
```
